Language-Based Security for Low-Level MPC

### 2024-07-21 ppdp24/example-bdoz.tex
checkpoint

With these conventions, a BDOZ library is defined in Figure
\ref{fig-bdoz} and a multiplication protocol to compute $\sx{x}{1} *
\sx{y}{2}$ is defined in Figure \ref{fig-beaver}. The latter is
malicious secure assuming that client 1 is trusted. Initially, in
calls to $\ttt{sum\_she}$ each party computes the sum of their shares
of $\sx{x}{1} + \macgv{\mesg{a}}$ and $\sx{y}{2} + \macgv{\mesg{b}}$,
and non-interactively computes the associated MACs and keys in the
SHE authentication scheme. These values are then
securely opened on client 1, which authenticates client
2's share via a call to $\ttt{auth}$ that $\ttt{assert}$s
the BDOZ authentication property. Note that the
opening of $\sx{y}{2} + \macgv{\mesg{b}}$ reveals no
information to client 1 about $\sx{y}{2}$ since $\macgv{\mesg{b}}$ is
in a unform random distribution by assumption. It is
also malicious secure since cheating is detected
by the $\ttt{assert}$.

>>>>

With these conventions, a BDOZ library is defined in Figure
\ref{fig-bdoz} and a multiplication protocol to compute $\sx{x}{1} *
\sx{y}{2}$ is defined in Figure \ref{fig-beaver}. The latter is
malicious secure assuming that client 1 is trusted. Initially, in
calls to $\ttt{sum\_she}$ each party computes the sum of their shares
of $\sx{x}{1} + \macgv{\mesg{a}}$ and $\sx{y}{2} + \macgv{\mesg{b}}$,
and non-interactively computes the associated MACs and keys in the
SHE authentication scheme. These values are then
securely opened on client 1, which authenticates client
2's share via a call to $\ttt{auth}$ that $\ttt{assert}$s
the BDOZ authentication property. Note that the
opening of $\sx{y}{2} + \macgv{\mesg{b}}$ reveals no
information to client 1 about $\sx{y}{2}$ since $\macgv{\mesg{b}}$ is
in a uniform random distribution by assumption. It is
also malicious secure since any cheating is detected
by the $\ttt{assert}$.
